Finiteness in Cubical Type Theory

### 2020-01-15 paper.tex
more

Homotopy Type Theory \cite{hottbook} further adds to this story in two ways.
First, its universe of types includes non-sets: whether or not a finiteness
predicate includes these gives us another dimension on which to discriminate.
Secondly,

classifying these types as
finite or not adds

can step in.
Through primarily a generalisation of equality, we gain access to a number of
exotic types which can, among other things, allow us to perform this ``hiding''.
In the context of finiteness, the act of hiding is worth studying in its own
right, and further delineates several new finiteness predicates which collapse
even in standard

>>>>

Homotopy Type Theory \cite{hottbook} further adds to this story in two ways.
First, its universe of types includes non-sets: whether or not a finiteness
predicate includes these gives us another dimension on which to discriminate.

The second addition is concerned with the hiding of information.
Occasionally in a constructive setting you don't want to have to reveal how you
proved something.
To model logical disjunction, for instance, we usually use a disjoint union: the
model isn't entirely correct, though, because a proof of \(A \text{or} B\)
reveals which of \(A\) or \(B\) we actually proved.

logical disjunction, for instance, is usually modelled with a
disjoint union.
This always means, however, that to prove ``A or B'' you have to reveal which of
A or B you did prove.
